---
title: "shinyblog"
author: "Omar Tabuni"
date: "3/9/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown

This blog is about how crate a shiny app using cereal products.
The graphs will illustrate the 
Nutritional Correlation In Cereal Products: 
between Micro and Macro Nutritions: 


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:
First step is the UR.R 
## UR.R
```{r cars}
library(shiny)
library(rsconnect)
library(dplyr)
library(ggplot2)
library(stringr)
 Define UI for application that draws a histogram
  my_ui <- fluidPage(
  
  titlePanel("Nutrition Correlation In Cereal Products "),
  
  # Sidebar with a slider input for number of bins 
  sidebarLayout(
    sidebarPanel(
     
                   radioButtons("cereal", label = h3("Macronutrients "),
                                choices = c("fat", "carbo", "protein", "sodium"),
                                selected = "fat"),
                   selectInput("select", label = h3("Micronutrients"), 
                               choices = list("fiber", "vitamins", "sugars",  "potass"), 
                               selected = 1),
                  
                   selectInput("background", label = h3("backround color"), 
                              choices = list("grey", "yellow"), 
                              selected = 1),
                   hr(),
                   fluidRow(column(3, verbatimTextOutput("value")))
       
    

    ),
    # Show a plot of the generated distribution
    mainPanel( 
      plotOutput("myPlot")
      
    )
  )
)

shinyUI(my_ui)

#hi
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
library(shiny)
library(rsconnect)
library(dplyr)
library(ggplot2)
library(stringr)

data1 <- read.csv("cereal.tsv", sep = "\t", header =TRUE)
# Define server logic required to draw a histogram
my_server <- function(input, output) {
  output$myPlot <- renderPlot({
    x <- input$select
    y <- input$cereal

    val1 <- select(data1, x)
    val2 <- select(data1, y)
    val3 <- input$background

  ggplot((data=data1), aes(val1, val2)) + geom_point() + theme(plot.background = element_rect(fill = val3, colour = 'grey')) + xlab(x) + ylab(y)
    
  #output$value <- renderPrint({ input$radio })
  #output$value <- renderPrint({ input$select })
  
 

    
 
  
})
}
shinyServer(my_server)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
